Work Fragmentation in Developer Interaction Data

### 2016-03-28 paper_2.tex
Cliff's delta RQ1 and fix RQ2
Cliff's delta RQ3
Fix cliff's delta
Minor changes

the results differ between Mylyn and UDC because in average there are more interruptions per session in the former. Then, for each group, we display the distribution of events per minute and edit ratio via boxplots. We can see the results with Mylyn in Figure \ref{fig:box_int_events}), and for UDC in Figure \ref{fig:box_int_events_udc}.

@@

With UDC, the results show a similar pattern in comparison with the results with Mylyn. When facing zero interruptions the editions and selections per minute are greater than with one or more interruptions, and as more interruptions occur this metrics gradually decrease. The difference between sessions with no interruptions and at least one is less marked in the edit per minute metric, but the selections per minute metric is more alike to the Mylyn results.

@@

More importantly, we used \textit{Cohen's d} to measure the practical significance of these results in term of effect size % the effect size of the differences in means as standardized difference~
\cite{C94}. \textit{Cohen's thresholds} are defined as follows: trivial ($<0.2$), small  ($\langle 0.2 - 0.5 ]$), moderate ($\langle 0.5 - 0.8 ]$) and large effect ($> 0.8$). As shown in Table \ref{tbl:p_value}, we note that the effect size of the interruptions over the number of edits by minute is (very) large. In selections, the effect is moderate for sessions having up three interruptions, and large to very large for sessions with over four interruptions. This reinforces our impressions that interruptions and user activity follow inverse relationships, and that they are quite pronounced.

@@

   & none & $\leq 3$ & $[4 - 5]$ & $[6 - 10]$ & $\geq 11$  \\  
  \hline
  \multicolumn{6}{c}{\textbf{Edits}} \\
  \hline
  mean & 6.29 &	2.59 & 1.55 & 1.29 & 0.91  \\ 
  % \cline{3-6} 
  %t.test & $\hookrightarrow$& \multicolumn{4}{c}{$<$ 2.2e-16} \\
   \cline{3-6} 
  U-test (adjusted) & $\hookrightarrow$ & \multicolumn{4}{c}{$<$ 2.2e-16} \\
  \cline{3-6} 
  Cohen's $d$ & $\hookrightarrow$	& \textbf{1.23} & \textbf{2.02} & \textbf{2.37} & \textbf{3.31}    \\
  \hline

@@

  \cline{3-6} 
  Cohen's $d$ & $\hookrightarrow$	& \textbf{0.66} & \textbf{1.17} & \textbf{1.93} & \textbf{1.78} \\  
\hline

  \multicolumn{6}{c}{\textbf{Edit ratio}} \\
  \hline 
  mean & 0.55 & 0.39 & 0.33 & 0.34 & 0.33 \\ 
  \cline{3-6} 
%    t.test & $\hookrightarrow$& 1.62E-13 & \multicolumn{3}{c}{$<$ 2.2e-16} \\
     \cline{3-6} 
    U-test (adjusted) & $\hookrightarrow$ & 4.2e-14& \multicolumn{3}{c}{$<$ 2.9e-16} \\
    \cline{3-6} 
    Cohen's $d$ & $\hookrightarrow$ & \textbf{0.84} & \textbf{1.33} & \textbf{1.48} & \textbf{2.12} \\ 
\hline

@@

		& none & $\leq 2$ & $[3 - 4]$ & $[5 - 7]$ & $\geq 7$  \\  
		\hline
		\multicolumn{6}{c}{\textbf{Edits}} \\
		\hline
		mean & 3.97 &	2.18 & 1.82 & 1.70 & 1.59 \\ 
		% \cline{3-6} 
		%t.test & $\hookrightarrow$& \multicolumn{4}{c}{$<$ 2.2e-16} \\
		\cline{3-6} 
		U-test (adjusted) & $\hookrightarrow$ & \multicolumn{4}{c}{$<$ 2.2e-16} \\
		\cline{3-6} 
		Cohen's $d$ & $\hookrightarrow$	& \textbf{0.58} & \textbf{0.88} & \textbf{1.05} & \textbf{1.35}    \\

		\hline
		\multicolumn{6}{c}{\textbf{Selections}} \\
		\hline 
		mean & 3.10 &	2.93 & 1.80 & 1.77 & 1.63  \\ 
		% \cline{3-6} 
		%t.test & $\hookrightarrow$& 6.258e-08 & 1.623e-12 & 4.87e-16 & $<$ 2.2e-16 \\
		\cline{3-6} 
		U-test (adjusted)& $\hookrightarrow$ & \multicolumn{4}{c}{$<$ 2.2e-16} \\
		\cline{3-6} 
		Cohen's $d$ & $\hookrightarrow$	& \textbf{0.44} & \textbf{0.66} & \textbf{0.81} & \textbf{0.85} \\  
		\hline

		\multicolumn{6}{c}{\textbf{Edit ratio}} \\
		\hline 
		mean & 0.68 & 0.56 & 0.55 & 0.54 & 0.57 \\ 
		\cline{3-6} 
		%    t.test & $\hookrightarrow$& 1.62E-13 & \multicolumn{3}{c}{$<$ 2.2e-16} \\
		\cline{3-6} 
		U-test (adjusted) &  $\hookrightarrow$& \multicolumn{4}{c}{$<$ 0.0001} \\
		\cline{3-6} 
		Cohen's $d$ & $\hookrightarrow$ & \textbf{0.37} & \textbf{0.46} & \textbf{0.49} & \textbf{0.55} \\ 
		\hline

@@

We tested the statistical significance of this results and show the results in the Table \ref{tbl:effect_size_dur_mylyn} for Mylyn, and Table \ref{tbl:effect_size_dur_udc} for UDC. For every group according to the number of interruptions, we measured the effect between the low and high groups of sessions, with the Cliff's delta test and U-test. The groups with one to three interruptions have moderate size effects, in comparison with the other groups with more interruptions that have lower size effects; this matches our observations via visual inspection on a more defined difference between the low and high groups when having a small number of interruptions. Starting from (approximately) three interruptions, the distributions of the metrics are very alike, except in some cases like the edit ratio with seven interruptions in Mylyn, where the median is almost the same but the distribution of the values are different enough to have a medium effect size. The bold numbers are those with a significant effect size.

\begin{table}[ht!]
	\tiny
	\renewcommand{\arraystretch}{1.3}
	\caption{Effect size and statistical significance of the relationships between edits and selection per minute, edit ratio, and duration of interruptions in Mylyn} %, and editions and selections.}
	\label{tbl:effect_size_dur_mylyn}
	\centering
	\begin{tabular}{l | p{1cm} | p{1cm} | p{1cm} | p{1cm} | p{1cm} | p{1cm} | p{1cm}} 
		Group & 1 & 2 & 3 & 4 & 5 & 6 & 7  \\  
		\hline
		\multicolumn{8}{c}{\textbf{Edits}} \\
		\hline
		U-test (adjusted) & \textbf{5.6e-10} & \textbf{6.5e-07} & \textbf{2.9e-04} & 0.0074 & 0.0021 & 0.32 &  0.39\\
		\hline
		Cliff's delta & 0.36 & 0.28 & 0.23 & 0.16 & 0.26 & 0.08 & -0.09 \\
		\hline

		\multicolumn{8}{c}{\textbf{Selections}} \\
		\hline 
		U-test (adjusted) & 0.0004 & 0.0047 & 0.0072 & 0.003 & 0.7014 & 0.0520 & 0.1284 \\
		\hline
		Cliff's delta & 0.22 & 0.16 & 0.17 & 0.20 & 0.03 & 0.16 & 0.18  \\  
		\hline

		\multicolumn{8}{c}{\textbf{Edit ratio}} \\
		\hline 
		U-test (adjusted) & \textbf{2.6e-06} & \textbf{5.7e-05} & 0.023 & \textbf{0.64} & 0.023 & 0.49 & 0.15 \\
		\hline 
		Cliff's delta & 0.28 & 0.23 & 0.15 & 0.03 & 0.20 & -0.06 & -0.17  \\
		\hline

@@

\begin{table}[ht!]
	\tiny
	\renewcommand{\arraystretch}{1.3}
	\caption{Effect size and statistical significance of the relationships between edits and selection per minute, edit ratio, and duration of interruptions in UDC} %, and editions and selections.}
	\label{tbl:effect_size_dur_udc}
	\centering
	\begin{tabular}{l | p{1cm} | p{1cm} | p{1cm} | p{1cm} | p{1cm} | p{1cm} | p{1cm}} 
		Group & 1 & 2 & 3 & 4 & 5 & 6 & 7  \\  
		\hline
		\multicolumn{8}{c}{\textbf{Edits}} \\
		\hline
		U-test (adjusted) & \textbf{1.9e-20} & \textbf{4.0e-13} & 0.0011 & 0.027 & \textbf{7.2e-08} & 0.055 & 6.5e-06\\
		\hline
		Cliff's delta & 0.36 & 0.28 & 0.22 & 0.16 & 0.26 & 0.08 & -0.09 \\
		\hline

		\multicolumn{8}{c}{\textbf{Selections}} \\
		\hline 
		U-test (adjusted) & \textbf{2.9e-07} & \textbf{2.3e-11} & 0.32 & 0.12 & 0.0043 & 0.45 & 0.12 \\
		\hline
		Cliff's delta & 0.22 & 0.17 & 0.17 & 0.20 & 0.03 & 0.16 & 0.17 \\  
		\hline

		\multicolumn{8}{c}{\textbf{Edit ratio}} \\
		\hline 
		U-test (adjusted) & \textbf{3.5e-05} & 0.033 & 0.033 & 0.20 & 0.004 & 0.14 & 0.0059 \\
		\hline 
		Cliff's delta & 0.28 & 0.23 & 0.15 & 0.03 & 0.20 & -0.06 & -0.16  \\
		\hline

@@

  \cline{3-4} 
  Cohen's $d$ & $\hookrightarrow$	& \textbf{0.16} & \textbf{0.24}   \\
  \hline

  \multicolumn{4}{c}{\textbf{after}} \\
  \hline 
  mean & 0.34 &	0.37 &	0.39 \\ 
   \cline{3-4} 
  U-test (adjusted) & $\hookrightarrow$ & 4.40e-16 & $<$ 5.67e-16 \\  
  \cline{3-4} 
  Cohen's $d$ & $\hookrightarrow$	& \textbf{0.14} & \textbf{0.22}  \\  
\end{tabular}
\end{table}

@@

We used Cohen's $d$, a parametric effect size measure, as it has defined thresholds allowing easier interpretation of the results. Other effect size measures such as the common language effect size \cite{KMW92} or $A_{12}$ \cite{RRT12} may slightly alter the discussion.

>>>>

The thresholds slightly differ between the datasets because there are more interruptions per session (in average) in Mylyn. After setting the ranges, for each group, we display the distribution of events per minute and edit ratio via boxplots. We can see the results with Mylyn in Figure \ref{fig:box_int_events}), and for UDC in Figure \ref{fig:box_int_events_udc}.

@@

With UDC, the results show a similar pattern in comparison with the results with Mylyn. When facing zero interruptions the editions and selections per minute are greater than in sessions with one or more interruptions, and as more interruptions occur this metrics gradually decrease. There is a big difference between sessions with no interruptions and at least one in the edit per minute metric, but compared to Mylyn the effect is smaller. The results with the selections per minute are more alike to the Mylyn results.

@@

More importantly, we used \textit{Cliff's delta} to measure the practical significance of these results in term of effect size % the effect size of the differences in means as standardized difference~
\cite{C94}. \textit{Cliff's delta thresholds} are defined as follows: negligible ($<0.147$), small  ($<0.33$), moderate ($<0.476$) and large effect otherwise. As shown in Table \ref{tbl:p_value}, we note that the effect size of the interruptions over the number of edits by minute is large. In selections, the effect is moderate for sessions having up three interruptions, and large for sessions with over four interruptions. This reinforces our impressions that interruptions and user activity follow inverse relationships, and that they are quite pronounced.

@@

   & none & $\leq 3$ & $[4 - 5]$ & $[6 - 10]$ & $\geq 11$  \\  
  \hline
  \multicolumn{6}{c}{\textbf{Edits}} \\
  \hline
  mean & 6.29 &	2.59 & 1.55 & 1.29 & 0.91  \\ 
  % \cline{3-6} 
  %t.test & $\hookrightarrow$& \multicolumn{4}{c}{$<$ 2.2e-16} \\
   \cline{3-6} 
  U-test (adjusted) & $\hookrightarrow$ & \multicolumn{4}{c}{$<$ 2.2e-16} \\
  \cline{3-6} 
  Cliff's delta & $\hookrightarrow$	& \textbf{0.61} & \textbf{0.77} & \textbf{0.80} & \textbf{0.87}    \\
  \hline

@@

  \cline{3-6} 
  Cliff's delta & $\hookrightarrow$	& \textbf{0.45} & \textbf{0.60} & \textbf{0.72} & \textbf{0.82} \\  
\hline

  \multicolumn{6}{c}{\textbf{Edit ratio}} \\
  \hline 
  mean & 0.55 & 0.39 & 0.33 & 0.34 & 0.33 \\ 
  \cline{3-6} 
%    t.test & $\hookrightarrow$& 1.62E-13 & \multicolumn{3}{c}{$<$ 2.2e-16} \\
     \cline{3-6} 
    U-test (adjusted) & $\hookrightarrow$ & 4.2e-14& \multicolumn{3}{c}{$<$ 2.9e-16} \\
    \cline{3-6} 
    Cliff's delta & $\hookrightarrow$ & \textbf{0.47} & \textbf{0.66} & \textbf{0.67} & \textbf{0.73} \\ 
\hline

@@

		& none & $\leq 2$ & $[3 - 4]$ & $[5 - 7]$ & $\geq 7$  \\  
		\hline
		\multicolumn{6}{c}{\textbf{Edits}} \\
		\hline
		mean & 3.97 &	2.18 & 1.82 & 1.70 & 1.59 \\ 
		% \cline{3-6} 
		%t.test & $\hookrightarrow$& \multicolumn{4}{c}{$<$ 2.2e-16} \\
		\cline{3-6} 
		U-test (adjusted) & $\hookrightarrow$ & \multicolumn{4}{c}{$<$ 2.2e-16} \\
		\cline{3-6} 
		Cliff's delta & $\hookrightarrow$	& \textbf{0.42} & \textbf{0.53} & \textbf{0.57} & \textbf{0.63}    \\

		\hline
		\multicolumn{6}{c}{\textbf{Selections}} \\
		\hline 
		mean & 3.10 &	2.93 & 1.80 & 1.77 & 1.63  \\ 
		% \cline{3-6} 
		%t.test & $\hookrightarrow$& 6.258e-08 & 1.623e-12 & 4.87e-16 & $<$ 2.2e-16 \\
		\cline{3-6} 
		U-test (adjusted)& $\hookrightarrow$ & \multicolumn{4}{c}{$<$ 2.2e-16} \\
		\cline{3-6} 
		Cliff's delta & $\hookrightarrow$	& \textbf{0.29} & \textbf{0.38} & \textbf{0.39} & \textbf{0.49} \\  
		\hline

		\multicolumn{6}{c}{\textbf{Edit ratio}} \\
		\hline 
		mean & 0.68 & 0.56 & 0.55 & 0.54 & 0.57 \\ 
		\cline{3-6} 
		%    t.test & $\hookrightarrow$& 1.62E-13 & \multicolumn{3}{c}{$<$ 2.2e-16} \\
		\cline{3-6} 
		U-test (adjusted) &  $\hookrightarrow$& \multicolumn{4}{c}{$<$ 0.0001} \\
		\cline{3-6} 
		Cliff's delta & $\hookrightarrow$ & \textbf{0.19} & \textbf{0.24} & \textbf{0.28} & \textbf{0.26} \\ 
		\hline

@@

We tested the statistical significance of this results and show the results in the Table \ref{tbl:effect_size_dur_mylyn} for Mylyn, and Table \ref{tbl:effect_size_dur_udc} for UDC. For every group according to the number of interruptions, we measured the effect between the low and high groups of sessions, with the Cliff's delta test and U-test. The groups with one to three interruptions have moderate size effects, in comparison with the other groups with more interruptions that have lower size effects; this matches our observations via visual inspection on a more defined difference between the low and high groups when having a small number of interruptions. Starting from (approximately) three interruptions, the distributions of the metrics are very alike, except in some cases like the edit ratio with seven interruptions in Mylyn, where the median is almost the same but the distribution of the values are different enough to have a medium effect size.

\begin{table}[ht!]
	\tiny
	\renewcommand{\arraystretch}{1.3}
	\caption{Effect size and statistical significance of the relationships between edits and selection per minute, edit ratio, and duration of interruptions in Mylyn} %, and editions and selections.}
	\label{tbl:effect_size_dur_mylyn}
	\centering
	\begin{tabular}{l | p{1cm} | p{1cm} | p{1cm} | p{1cm} | p{1cm} | p{1cm} | p{1cm}} 
		Group & 1 & 2 & 3 & 4 & 5 & 6 & 7  \\  
		\hline
		\multicolumn{8}{c}{\textbf{Edits}} \\
		\hline
		U-test (adjusted) & 5.6e-10 & 6.5e-07 & 2.9e-04 & 0.0074 & 0.0021 & 0.32 &  0.39\\
		\hline
		Cliff's delta & \textbf{0.36} & \textbf{0.26} & \textbf{0.23} & \textbf{0.16} & \textbf{0.26} & \textbf{0.08} & \textbf{-0.09} \\
		\hline

		\multicolumn{8}{c}{\textbf{Selections}} \\
		\hline 
		U-test (adjusted) & 0.0004 & 0.0047 & 0.0072 & 0.003 & 0.7014 & 0.0520 & 0.1284 \\
		\hline
		Cliff's delta & \textbf{0.22} & \textbf{0.16} & \textbf{0.17} & \textbf{0.20} & \textbf{0.03} & \textbf{0.16} & \textbf{0.18}  \\  
		\hline

		\multicolumn{8}{c}{\textbf{Edit ratio}} \\
		\hline 
		U-test (adjusted) & 2.6e-06 & 5.7e-05 & 0.023 & 0.64 & 0.023 & 0.49 & 0.15 \\
		\hline 
		Cliff's delta & \textbf{0.28} & \textbf{0.23} & \textbf{0.15} & \textbf{0.03} & \textbf{0.20} & \textbf{-0.06} & \textbf{-0.17}  \\
		\hline

@@

\begin{table}[ht!]
	\tiny
	\renewcommand{\arraystretch}{1.3}
	\caption{Effect size and statistical significance of the relationships between edits and selection per minute, edit ratio, and duration of interruptions in UDC} %, and editions and selections.}
	\label{tbl:effect_size_dur_udc}
	\centering
	\begin{tabular}{l | p{1cm} | p{1cm} | p{1cm} | p{1cm} | p{1cm} | p{1cm} | p{1cm}} 
		Group & 1 & 2 & 3 & 4 & 5 & 6 & 7  \\  
		\hline
		\multicolumn{8}{c}{\textbf{Edits}} \\
		\hline
		U-test (adjusted) & 1.9e-20 & 4.0e-13 & 0.0011 & 0.027 & 7.2e-08 & 0.055 & 6.5e-06\\
		\hline
		Cliff's delta & \textbf{0.36} & \textbf{0.27} & \textbf{0.08} & \textbf{0.06} & \textbf{0.17} & \textbf{0.07} & \textbf{0.18} \\
		\hline

		\multicolumn{8}{c}{\textbf{Selections}} \\
		\hline 
		U-test (adjusted) & 2.9e-07 & 2.3e-11 & 0.32 & 0.12 & 0.0043 & 0.45 & 0.12 \\
		\hline
		Cliff's delta & \textbf{0.20} & \textbf{0.25} & \textbf{0.02} & \textbf{0.05} & \textbf{0.10} & \textbf{0.03} & \textbf{0.07} \\  
		\hline

		\multicolumn{8}{c}{\textbf{Edit ratio}} \\
		\hline 
		U-test (adjusted) & 3.5e-05 & 0.033 & 0.033 & 0.20 & 0.004 & 0.14 & 0.0059 \\
		\hline 
		Cliff's delta & \textbf{0.17} & \textbf{0.08} & \textbf{0.05} & \textbf{0.04} & \textbf{0.10} & \textbf{0.06} & \textbf{0.11}  \\
		\hline

@@

  \cline{3-4} 
   Cliff's delta & $\hookrightarrow$	& \textbf{-0.05} & \textbf{-0.03}   \\
  \hline

  \multicolumn{4}{c}{\textbf{after}} \\
  \hline 
  mean & 0.34 &	0.37 &	0.39 \\ 
   \cline{3-4} 
  U-test (adjusted) & $\hookrightarrow$ & 4.40e-16 & $<$ 5.67e-16 \\  
  \cline{3-4} 
  Cliff's delta & $\hookrightarrow$	& \textbf{-0.03} & \textbf{-0.02}  \\  
\end{tabular}
\end{table}

@@

We used Cliff's delta, a non-parametric effect size measure, as it has defined thresholds allowing easier interpretation of the results. Other effect size measures such as the common language effect size \cite{KMW92} or $A_{12}$ \cite{RRT12} may slightly alter the discussion.
